Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/gen-graph-connected-heatmap.tex
Handle headers on first line
Green / blue instead of blood splatters

%% Thu 07 Apr 2016 11:12:14 BST

@@

  ffffffffffffffffffff846eff6f65ff846eff7e6cff6f65ff8c72ff7367ff7e6cff8c72ff7869ffffffffac88ff9576%
  ff9576ff7869ff8c72ffac88ff846eff9576ff9576ff9f7dff8c72ff9f7dff8c72ff9576ffac88ff9f7dff8c72ff8c72%
  ff8c72ff9576ff8c72ff9f7dff8c72ffffffff9f7dff9576ff9f7dff9576ff9576ff9576ff7e6cff9f7dff9f7dffffff%
  ff9f7dffac88ff9f7dffffffff7e6cffac88ffffffffffffffffffff9f7dff9f7dffffffffffffffac88ffac88ffac88%
  ff9576ffac88ffffffffac88ffffffffffffff9f7dffac88ff9f7dffffffff9f7dffac88ff9f7dff9576ff6f65ff7869%
  ff7e6cfc6260fc6260ff6b63ac0527ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffac88%
  ffffffffffffffac88ffac88ffffffffac88ff9f7dffffffff9f7dee4156ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffac88ffac88ffffffffac88ff9f7ded4155ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7d%
  ff8c72ff9f7dff9f7dec3f55ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9576ffffffff9f7dffffff%
  ffac88ffffffffac88ff9f7dff9f7dff9576ff9f7dffac88e93c53ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ffac88ffffffff9f7dff8c72ff9576ff9f7dff9f7dff9f7dffffffffffffec4055ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffff7e6cffac88ffac88ff7e6cff9f7d%
  ff9f7dff9576e33450ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffffffff9576%
  ffac88ff846effac88ffac88ffac88ffac88ff9576ec3f55ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffac88ffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffac88ffac88%
  ff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9576ffac88ffac88ffac88ee4156ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffff9576%
  ffac88ffffffff9f7dff9f7dffac88ffac88ff9f7dff9f7dff9576ffffffff9f7dff9576ffffffff9576ffffffff9f7d%
  ffac88e1314fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ff9f7dff9f7dffac88ff8c72ff7e6c%
  ff9576ffffffff9576ff9576ff846eff9576de2e4dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ffac88ffffffffffffffffffff9f7dffac88ff9f7dff9f7dffffffff9f7dff9f7dff8c72ffac88ffffffff9576ff9f7d%
  ff9f7dff8c72ffffffff9576ffffffff8c72ffac88ffffffffffffff8c72ff9576dd2d4dffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffff9f7dff9f7dffac88%
  ffffffffac88ff9576ffffffffac88ff9576ffac88ff9576ffac88ff9f7dff846effac88ff8c72ff846eff8c72ff8c72%
  d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffffffff%
  ffac88ffac88ffffffffac88ffffffffac88ff9576ff9f7dffac88ff9f7dffac88ffac88ff9f7dffac88ffac88ff9f7d%
  ff9f7dff9576ff9f7dff8c72ffac88da294bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ff9576ffac88ffac88%
  ffffffff9f7dff8c72ffac88ff9f7dffac88ff846effac88ff846efe6862da294bffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffac88ffac88ffac88ff9f7dffffffff8c72%
  ffac88ffffffffffffff9f7dffffffff9f7dff9f7dffac88ff8c72ff8c72ffffffff9576ff7869ff7367ff8c72d7264a%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffac88ffffff%
  ffffffffac88ffffffffac88ffffffff9f7dffac88ff9f7dff9f7dffac88ffffffff9f7dff9f7dff7e6cff9576ff9f7d%
  ff9576ff7869ff7869ff6f65d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffac88ffffffffffffffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dff9f7dff9f7dff9f7dff9f7dffffff%
  ff9f7dff9576ff8c72ff9576ff9576ff7869ff7e6cf6545cfc6260d52349ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffff9f7dffffffffffffff8c72ff9f7dffac88ff9576%
  ffac88ff9576ff8c72ff9f7dff9f7dff9f7dff8c72ff9576ff6f65ff846eff6f65ff6b63fd6561fd6561d21f47ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffff%
  ffffffffffffffffffffffffff9f7dff9f7dff8c72ff9f7dffffffffac88ff9576ff7e6cff846eff846efe6862ff6b63%
  fe6862f7565cfc6260d8264affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88ffffffffac88%
  ffffffffffffff9576ffffffffac88ffac88ff9f7dffffffffac88ff8c72ffffffff9576ffac88ffac88ffac88ff7367%
  ff6f65ff7e6cfe6862fe6862f7585dfb605ffe6862f95c5ed32148ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9576ffac88ff9f7dffffffff9f7d%
  ff9f7dff9f7dff9576ff7e6cff8c72ff9576ff6f65ff6b63ff6b63fb605ffd6561ff6b63f85a5dda294bffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ff9f7dff9f7dffac88ffac88%
  ffffffffffffff9f7dff9f7dff9f7dffac88ff9f7dff9576ff6f65ff8c72ff7e6cff6b63fe6862ff6f65f34d59fe6862%
  f85a5dff6f65d7254affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffff%
  ffac88ffac88ff9f7dffac88ffac88ff9576ff8c72ff9576ffac88ff9576ff846eff9576ff8c72ff846efa5e5ffb605f%
  fa5e5ff7585dfb605ff7565cf85a5dfe6862fc6260d8264affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffffff%
  ffffffff9576ffffffffac88ffffffffffffffac88ffac88ffac88ff8c72ff9f7dff8c72ffac88ff8c72ff846eff7869%
  ff7e6cfd6561fd6561fd6561fa5e5ffd6561fa5e5fff6b63f85a5dfd6561fb605fff7e6ce1314fffffffffffffffffff%
  ffffffffffffffffffffffffffffffff9f7dffac88ff9576ffac88ffac88ffffffffac88ffffffff9f7dff7e6cff9576%
  ff7367ffac88ff7869ff7869fe6862ff6b63fc6260fd6561ff7367fe6862fc6260fe6862f85a5df7585dfe6862ff6f65%
  ff6b63e73952ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffac88ffffffffffffffffffffffffffac88ffffffff9f7dffac88ffac88ff9f7dff9576%
  ffffffff9576ffac88ff8c72ff846eff9576ff846eff6f65ff846eff846eff7367f85a5dfb605ffc6260f7585df7565c%
  fd6561ff7367ff6f65fe6862ff7e6cff846eef4356ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffac88ffffffffac88ffffff%
  ffac88ff9f7dff9576ffffffffffffff8c72ffac88ff9576ff9576ff9576ff9576ff9576ff9f7dff7e6cff846efe6862%
  ff7869ff8c72fe6862ff6b63ff7367ff7869ff8c72ff846eff846eff9576ff9f7de83b53ffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88%
  ffffffffac88ffac88ffffffffffffffffffff9576ff9f7dff8c72ff9576ff9f7dff846effac88ff9576ff8c72ffac88%
  ff7e6cff7e6cff8c72ff8c72ff6b63ff846eff6f65ff7869ff7367ff9f7dff9576ff7e6cff846eff9f7dff8c72ff8c72%
  ed4155ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9f7dff9576ff846eff9f7dffac88ff8c72ffac88%
  ff9576ff9576ff9f7dff846eff8c72ff7e6cfe6862ff6f65fc6260ff9576ff8c72ff846eff7e6cff9576ff9f7dff9576%
  ffffffff8c72ffac88ffac88ffac88f24a59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffff8c72ffffffff9f7dff9576%
  ff8c72ff9f7dffac88ffac88ff9f7dff846eff7869ff9f7dff7e6cff7e6cff7367ff6f65fd6561ff7e6cfe6862fe6862%
  ff9576ff8c72ff9f7dff846effffffff9f7dff9f7dff9f7dffac88ffffffe93c53ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dff9f7d%
  ffffffff9f7dff9576ff9f7dffac88ffac88ff9576ff8c72ff9f7dff9f7dff846efe6862ff6b63fd6561ff7367f95c5e%
  fe6862ff6f65ff846eff7e6cff7869ff6b63ff846eff9f7dff9f7dff846eff8c72ff9f7dff8c72ffffffff9f7df34d59%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ff9f7dff7e6cff8c72ff9576ff8c72ff846eff8c72ff8c72%
  fd6561ff7e6cfc6260ff846eff7869fd6561f95c5ef95c5eff6f65ff7e6cff9f7dff846eff9576ff9f7dff9576ffac88%
  ffac88ff8c72ff9576ff9f7def4457ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9f7dff9576ff8c72ff9f7d%
  ff8c72ff7367ff8c72fe6862ff7367ff6b63fb605ffc6260fe6862f85a5dfd6561f7565cff6f65fe6862ff6f65ff7869%
  ff8c72ff9576ff8c72ff9576ffac88ffffffffac88ffac88ff9f7df14858ffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffac88ffac88%
  ff8c72ff7869ff9f7dff9f7df95c5eff7869fe6862fd6561ff7367fa5e5ff95c5ef7565cf5515bf6545cf7585dfc6260%
  fb605fff6f65fc6260ff6f65ff6b63ff846eff8c72ff9f7dff9576ffac88ffac88ffac88ff9576ffac88ef4356ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
  ff9576ffac88ffac88ff7367ff846eff7367fe6862ff6f65fb605ffd6561f95c5eff6f65f7585dff6b63f95c5ef85a5d%
  f7565cf24a59f5535bf4505aff6b63f7585dfa5e5fff6f65ff6b63ff7e6cff8c72ff8c72ffac88ff9f7dff9f7dff8c72%
  ffffffff8c72ff846ef14958ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffff%
  ffac88ffffffffffffffffffffac88ffac88ffac88ff9576ff9576ff7e6cff8c72ff7367f95c5eff7869f85a5dfb605f%
  fb605ff85a5df85a5dfc6260f6545cfa5e5ff7585dfd6561fa5e5ffc6260ff6b63ff7869ff7e6cff8c72fd6561ff846e%
  ffac88ffac88ff9f7dffac88ff9576ff9f7dff9576ff846ef7585dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffffff846eff8c72ff7e6cff846eff7e6c%
  ff6f65fb605ffe6862ff6b63fc6260f95c5efb605ff85a5df7585dfa5e5ffd6561fe6862fb605ffd6561fe6862ff6b63%
  ff6f65ff846eff7e6cff9f7dff8c72ff9576ff9f7dffac88ff9576ff9576ffac88ff9f7dffac88f24b59ffffffffffff%

>>>>

%% Wed 20 Apr 2016 12:04:43 AEST

@@

  ffffffffffffffffff6cc78c5ab5896cc78c67c28b5ab58972cd8d5eb98a67c28b72cd8d62bd8bffffff9cea9c79d48d%
  79d48d62bd8b72cd8d9cea9c6cc78c79d48d79d48d85de9172cd8d85de9172cd8d79d48d9cea9c85de9172cd8d72cd8d%
  72cd8d79d48d72cd8d85de9172cd8dffffff85de9179d48d85de9179d48d79d48d79d48d67c28b85de9185de91ffffff%
  85de919cea9c85de91ffffff67c28b9cea9cffffffffffffffffff85de9185de91ffffffffffff9cea9c9cea9c9cea9c%
  79d48d9cea9cffffff9cea9cffffffffffff85de919cea9c85de91ffffff85de919cea9c85de9179d48d5ab58962bd8b%
  67c28b4da9874da98756b289233281ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffff85de919cea9c%
  ffffffffffff9cea9c9cea9cffffff9cea9c85de91ffffff85de91228b82ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffff9cea9c9cea9c9cea9c9cea9cffffff9cea9c85de91208a82ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c9cea9c85de91%
  72cd8d85de9185de911e8982ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  9cea9cffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff79d48dffffff85de91ffffff%
  9cea9cffffff9cea9c85de9185de9179d48d85de919cea9c1e8582ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
  ffffff9cea9c9cea9c9cea9cffffff85de9172cd8d79d48d85de9185de9185de91ffffffffffff1f8a82ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff%
  ffffffffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffff67c28b9cea9c9cea9c67c28b85de91%
  85de9179d48d1f7c82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de91ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff9cea9cffffff9cea9c9cea9cffffffffffff79d48d%
  9cea9c6cc78c9cea9c9cea9c9cea9c9cea9c79d48d1e8982ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffff9cea9c9cea9cffffffffffff9cea9cffffff9cea9c85de919cea9c85de919cea9c9cea9c%
  85de91ffffffffffffffffff9cea9c9cea9c9cea9c85de9179d48d9cea9c9cea9c9cea9c228b82ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff79d48d%
  9cea9cffffff85de9185de919cea9c9cea9c85de9185de9179d48dffffff85de9179d48dffffff79d48dffffff85de91%
  9cea9c1f7881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c9cea9c85de9185de919cea9c72cd8d67c28b%
  79d48dffffff79d48d79d48d6cc78c79d48d1f7481ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
  9cea9cffffffffffffffffff85de919cea9c85de9185de91ffffff85de9185de9172cd8d9cea9cffffff79d48d85de91%
  85de9172cd8dffffff79d48dffffff72cd8d9cea9cffffffffffff72cd8d79d48d1f7381ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff9cea9cffffffffffff85de9185de919cea9c%
  ffffff9cea9c79d48dffffff9cea9c79d48d9cea9c79d48d9cea9c85de916cc78c9cea9c72cd8d6cc78c72cd8d72cd8d%
  216881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffffffffffffffff%
  9cea9c9cea9cffffff9cea9cffffff9cea9c79d48d85de919cea9c85de919cea9c9cea9c85de919cea9c9cea9c85de91%
  85de9179d48d85de9172cd8d9cea9c206e81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff9cea9c79d48d9cea9c9cea9c%
  ffffff85de9172cd8d9cea9c85de919cea9c6cc78c9cea9c6cc78c53af88206e81ffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffff85de91ffffffffffff9cea9c9cea9c9cea9c85de91ffffff72cd8d%
  9cea9cffffffffffff85de91ffffff85de9185de919cea9c72cd8d72cd8dffffff79d48d62bd8b5eb98a72cd8d206a81%
  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9c9cea9c9cea9cffffff%
  ffffff9cea9cffffff9cea9cffffff85de919cea9c85de9185de919cea9cffffff85de9185de9167c28b79d48d85de91%
  79d48d62bd8b62bd8b5ab589216881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff%
  9cea9cffffffffffffffffff85de91ffffff9cea9cffffffffffff9cea9c85de9185de9185de9185de9185de91ffffff%
  85de9179d48d72cd8d79d48d79d48d62bd8b67c28b3b9c854da987216781ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  9cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffff85de91ffffffffffff72cd8d85de919cea9c79d48d%
  9cea9c79d48d72cd8d85de9185de9185de9172cd8d79d48d5ab5896cc78c5ab58956b28950ac8850ac88226281ffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffff%
  ffffffffffffffffffffffff85de9185de9172cd8d85de91ffffff9cea9c79d48d67c28b6cc78c6cc78c53af8856b289%
  53af883e9d854da987206b81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff79d48dffffff9cea9cffffff9cea9c%
  ffffffffffff79d48dffffff9cea9c9cea9c85de91ffffff9cea9c72cd8dffffff79d48d9cea9c9cea9c9cea9c5eb98a%
  5ab58967c28b53af8853af88409f864aa78753af8845a286226481ffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c79d48d9cea9c85de91ffffff85de91%
  85de9185de9179d48d67c28b72cd8d79d48d5ab58956b28956b2894aa78750ac8856b28943a186206e81ffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c85de9185de919cea9c9cea9c%
  ffffffffffff85de9185de9185de919cea9c85de9179d48d5ab58972cd8d67c28b56b28953af885ab58931958453af88%
  43a1865ab589206981ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9cffffffffffff%
  9cea9c9cea9c85de919cea9c9cea9c79d48d72cd8d79d48d9cea9c79d48d6cc78c79d48d72cd8d6cc78c48a5864aa787%
  48a586409f864aa7873e9d8543a18653af884da987206b81ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff85de91ffffffffffff%
  ffffff79d48dffffff9cea9cffffffffffff9cea9c9cea9c9cea9c72cd8d85de9172cd8d9cea9c72cd8d6cc78c62bd8b%
  67c28b50ac8850ac8850ac8848a58650ac8848a58656b28943a18650ac884aa78767c28b1f7881ffffffffffffffffff%
  ffffffffffffffffffffffffffffff85de919cea9c79d48d9cea9c9cea9cffffff9cea9cffffff85de9167c28b79d48d%
  5eb98a9cea9c62bd8b62bd8b53af8856b2894da98750ac885eb98a53af884da98753af8843a186409f8653af885ab589%
  56b2891e8282ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9c9cea9c9cea9cffffffffffffffffffffffff9cea9cffffff85de919cea9c9cea9c85de9179d48d%
  ffffff79d48d9cea9c72cd8d6cc78c79d48d6cc78c5ab5896cc78c6cc78c5eb98a43a1864aa7874da987409f863e9d85%
  50ac885eb98a5ab58953af8867c28b6cc78c248d83ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff9cea9cffffff9cea9cffffff9cea9cffffff%
  9cea9c85de9179d48dffffffffffff72cd8d9cea9c79d48d79d48d79d48d79d48d79d48d85de9167c28b6cc78c53af88%
  62bd8b72cd8d53af8856b2895eb98a62bd8b72cd8d6cc78c6cc78c79d48d85de911e8482ffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9c%
  ffffff9cea9c9cea9cffffffffffffffffff79d48d85de9172cd8d79d48d85de916cc78c9cea9c79d48d72cd8d9cea9c%
  67c28b67c28b72cd8d72cd8d56b2896cc78c5ab58962bd8b5eb98a85de9179d48d67c28b6cc78c85de9172cd8d72cd8d%
  208a82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffff9cea9cffffff9cea9c85de919cea9c9cea9c85de9179d48d6cc78c85de919cea9c72cd8d9cea9c%
  79d48d79d48d85de916cc78c72cd8d67c28b53af885ab5894da98779d48d72cd8d6cc78c67c28b79d48d85de9179d48d%
  ffffff72cd8d9cea9c9cea9c9cea9c2e9384ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9cffffff72cd8dffffff85de9179d48d%
  72cd8d85de919cea9c9cea9c85de916cc78c62bd8b85de9167c28b67c28b5eb98a5ab58950ac8867c28b53af8853af88%
  79d48d72cd8d85de916cc78cffffff85de9185de9185de919cea9cffffff1e8582ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de9185de91%
  ffffff85de9179d48d85de919cea9c9cea9c79d48d72cd8d85de9185de916cc78c53af8856b28950ac885eb98a45a286%
  53af885ab5896cc78c67c28b62bd8b56b2896cc78c85de9185de916cc78c72cd8d85de9172cd8dffffff85de91319584%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
  ffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9c85de9167c28b72cd8d79d48d72cd8d6cc78c72cd8d72cd8d%
  50ac8867c28b4da9876cc78c62bd8b50ac8845a28645a2865ab58967c28b85de916cc78c79d48d85de9179d48d9cea9c%
  9cea9c72cd8d79d48d85de91268e83ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff85de91ffffffffffffffffff9cea9c9cea9c9cea9c85de9185de9179d48d72cd8d85de91%
  72cd8d5eb98a72cd8d53af885eb98a56b2894aa7874da98753af8843a18650ac883e9d855ab58953af885ab58962bd8b%
  72cd8d79d48d72cd8d79d48d9cea9cffffff9cea9c9cea9c85de912a9183ffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de91ffffff9cea9c9cea9c%
  72cd8d62bd8b85de9185de9145a28662bd8b53af8850ac885eb98a48a58645a2863e9d853799853b9c85409f864da987%
  4aa7875ab5894da9875ab58956b2896cc78c72cd8d85de9179d48d9cea9c9cea9c9cea9c79d48d9cea9c248d83ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffff9cea9c%
  79d48d9cea9c9cea9c5eb98a6cc78c5eb98a53af885ab5894aa78750ac8845a2865ab589409f8656b28945a28643a186%
  3e9d852e9384399a8535988456b289409f8648a5865ab58956b28967c28b72cd8d72cd8d9cea9c85de9185de9172cd8d%
  ffffff72cd8d6cc78c2c9283ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff%
  9cea9cffffffffffffffffff9cea9c9cea9c9cea9c79d48d79d48d67c28b72cd8d5eb98a45a28662bd8b43a1864aa787%
  4aa78743a18643a1864da9873b9c8548a586409f8650ac8848a5864da98756b28962bd8b67c28b72cd8d50ac886cc78c%
  9cea9c9cea9c85de919cea9c79d48d85de9179d48d6cc78c409f86ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
  ffffffffffffffffffffffffffffffffffffffffff85de919cea9cffffffffffff6cc78c72cd8d67c28b6cc78c67c28b%
  5ab5894aa78753af8856b2894da98745a2864aa78743a186409f8648a58650ac8853af884aa78750ac8853af8856b289%
  5ab5896cc78c67c28b85de9172cd8d79d48d85de919cea9c79d48d79d48d9cea9c85de919cea9c2f9484ffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff85de916cc78cffffff%
  6cc78c79d48d72cd8d62bd8b67c28b5eb98a5eb98a48a5864da987409f864aa7874aa78745a28653af884da9874aa787%
  62bd8b56b28953af885eb98a62bd8b72cd8d79d48d67c28b79d48d79d48d85de9185de9185de9172cd8d72cd8d62bd8b%
